\documentclass{article}
\usepackage[english]{babel}
\usepackage{tabularx}

\begin{document}
\setlength{\extrarowheight}{2pt}


% Title
\begin{center}
\textsc{\LARGE Mesa Robotics Organization} \\[0.4cm]
{\Large Meeting Minutes} \\[0.4cm]
{\large November 15, 2013} \\[0.3cm]
{\large San Diego Mesa College, K201-B} \\[1.0cm]
\end{center}


\begin{tabular}{>{\bfseries}r l}
Start Time & 11:30 AM \\
End Time & 1:10 PM
\end{tabular}


\section{Attendance}
\subsection[Present]{Members present:}
\begin{tabularx}{\textwidth}{r X}
President & Katie Swar \\
Vice President & Charles Bayley \\
Treasurer & Quan Doan \\
Enforcer & Foryst Cortopassi \\
Secretary & Nils Olsson \dotfill nilso@enosis.net \\
& Kemberlyn Rodrigues \\
& Ting Yu \\
& Brian Nguyen \\
& Devon Sallume \\
& Mega Loughmiller \\
& Alan Herrera \\
& Russel Humphrey \\
& Steven Button \\
& Danny Tran \\
& Joe Brennan
\end{tabularx}

\subsection[Absent]{Members absent:}

\section{ROSE Project}
\subsection{Document Drafting [11:30 AM]}
Professor Wesley brought up the current draft of the ROSE Project experiment 1 proposed details, orginally written up by Joe. As a group we discussed several sections of the document, improving the specificity of project descriptions and proposed implementations, in addition to correcting grammar. 

The proposed labratory will apply elements of physics and mathematics to a narrative. The construction of a well written narrative will be critical for the success of this project as an engaging and intriguing narrative will help bridge the physical gap between students and the actuall physical lab.

\subsection{Experiment Design [12:00 PM]}
A design sketch of the physics experiment was brought up on the screen to discuss design aspects of the experiment. Mechanical aspects, the bucket conveyor, the drop hatch and the ramp mechanisms were discussed.

A major question brought up for discussion: what rules do we intend to enforce in order to focus students towards achieving the proposed goal? Several posibilities were time restrictions, limits on the number of attempts, but most interesting were implications of failing upon the experiments later in a series of experiments: the strong posibilities for making a narrative game from a series of experiments, i.e. a campaign composed of scenarios.

\subsubsection{Project Areas [12:40 PM]}
\begin{enumerate}
    \item Bucket Conveyor
    \item Track Construction/Height Selector
    \item Target Area/Sensor
\end{enumerate}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document Finalization --- DO NOT TOUCH
\end{document}
